The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-05-20 background.tex
修改结构，开始写
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
new

\subsection{Origin and description of the research problem} % (fold)
\label{sub:origin_and_description_of_the_problem}

@@

(problems background to form the ecosystem)
% subsection origin_and_description_of_the_problem (end)

\subsection{Cloud manufacturing ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}

\subsubsection{Cloud manufacturing ecosystem architecture}

@@

\subsubsection{Operation model}
% 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
\begin{figure}[!h]
\centering\small
% \subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
% \subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
\resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
\label{fig:simpleorderflow}
\end{figure}
\subsubsection{Main features in the ecosystem}
% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
As shown in \autoref{fig:structure}, 
Rating system, decision support system, recommender system,
detail info will seen in
Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

% subsection cloud_manufacturing_ecosystem (end)

\subsection{Main complexity concepts} % (fold)
\label{sub:main_complexity_concepts}

\subsubsection{Self-organization}

\subsubsection{Emergence}

\subsubsection{Co-evolution}

\subsubsection{Adaption}
% subsection main_complexity_concepts (end)

\subsection{Ecosystem evolvement} % (fold)
\label{sub:ecosystem_evolvement}

% subsection ecosystem_evolvement (end)

\subsection{Optimal guidance} % (fold)
\label{sub:optimal_guidance}

% subsection optimal_guidance (end)
% section background (end)

>>>>

@@

(problems background to form the ecosystem)

\subsection{Cloud manufacturing} % (fold)
\label{sub:cloud_manufacturing}

\subsubsection{Cloud manufacturing architecture}

@@

\subsubsection{Operation model}
\label{ssub:operation_model}
% 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
\begin{figure}[htbp]
\centering
\subfloat[Demander]{\includegraphics[width=0.8\textwidth]{figures/demander_main_process}\label{fig:demanderprocess}}\\
\subfloat[Provider]{\includegraphics[width=0.8\textwidth]{figures/provider_main_process}\label{fig:providerprocess}}
\caption{Main operational processes}
\end{figure}

\begin{figure}[!h]
\centering\small
% \subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
% \subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
\resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
\label{fig:simpleorderflow}
\end{figure}

% subsection cloud_manufacturing(end)

% \subsection{Main complexity concepts} % (fold)
% \label{sub:main_complexity_concepts}

% \subsubsection{Self-organization}

% \subsubsection{Emergence}

% \subsubsection{Co-evolution}

% \subsubsection{Adaption}
% % subsection main_complexity_concepts (end)

\subsection{The evolution of manufacturing ecosystem} % (fold)
\label{sub:the_evolution_of_manufacturing_ecosystem}
Before the realization of the operation model mentioned above(\autoref{ssub:operation_model}), we will analyse the evolution path in both macro and micro view of manufacturing ecosystem w.r.t. the domain in cloud manufacturing..  
\subsubsection{Macroscopic evolution} % (fold)
\label{ssub:macroscopic_evolution}

% subsubsection microscopic_evolution (end)
\subsubsection{Microscopic evolution} % (fold)
\label{ssub:microscopic_evolution}

% subsubsection macroscopic_evolution (end)

\subsection{Main topics and their academic importance}
% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
As shown in \autoref{fig:structure}, 
Rating system, decision support system, recommender system,
detail info will seen in
Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

% subsection the_evolution_of_manufacturing_ecosystem (end)
% section background (end)
